Factorization Algebras and Factorization Homology on Stratified Spaces

### 2024-05-08 sections/2homology.tex
Removing mistake.

\begin{remark}
    For more details on $\mathbb{E}_n$-algebras and why these algebras encompass large portions of the examples one usually cares about see \cite[§5.1]{lurie_ha}. %or alternatively in appendix \Cref{app:En_algebras}. 
    Roughly speaking, $\mathbb{E}_1$-algebras are homotopy-associative algebras and with increasing $n$ we get increasing levels of homotopy commutativity, such that the colimit $\mathbb{E}_\infty$ parametrises homotopy-commtuative algebras. Having said that, the first part of the proposition is just the classical statement that the little $n$-disks operad and the little $n$-cubes operad are equivalent. Through \cite{lurie_tqft} and \cite{scheimbauer2014}, $\mathbb{E}_n$-algebras also serve as input for constructing fully extended TQFTs by using factorization homology.
\end{remark}

@@

\subsection{\texorpdfstring{$\otimes$}{tensor}-excision and Homology Theories}

>>>>

\begin{remark}
    For more details on $\mathbb{E}_n$-algebras and why these algebras encompass large portions of the examples one usually cares about see \cite[§5.1]{lurie_ha}. %or alternatively in appendix \Cref{app:En_algebras}. 
    Roughly speaking, $\mathbb{E}_1$-algebras are homotopy-associative algebras and with increasing $n$ we get increasing levels of homotopy commutativity, such that the colimit $\mathbb{E}_\infty$ parametrizes homotopy-commtuative algebras. Having said that, the first part of the proposition is just the classical statement that the little $n$-disks operad and the little $n$-cubes operad are weakly equivalent. Through \cite{lurie_tqft} and \cite{scheimbauer2014}, $\mathbb{E}_n$-algebras also serve as input for constructing fully extended TQFTs by using factorization homology.
\end{remark}

@@

\subsection{\texorpdfstring{$\otimes$}{tensor}-excision and Homology Theories}\label{sec:excision_homology}
